\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-10 paper.qmd
Added Figure 11 title

```{r}
#| label: fig-five-gau-projs
#| fig-height: 15
#| fig-width: 15
#| fig-pos: H
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"

>>>>

```{r}
#| label: fig-five-gau-projs
#| fig-height: 15
#| fig-width: 15
#| fig-pos: H
#| fig-cap: "Model in \\gD{}, on the layouts from tSNE, UMAP, and PaCMAP (a1, b1, c1). Two views of the fit in projections of each layout from $4\\text{-}D$, for the Gaussian cluster data. All \\gD{} models show five well-separated clusters with different gaps. Layout a1 shows small separations, while layout b2 shows large gaps. On the other hand, layout b3 shows average gaps with exact positions as in $4\\text{-}D$. Assessing the different models fit for different layouts for a specific cluster shows filled-out shape in a1, a2, and b1, b2. On the other hand, c1 and c2 shows pancake shape.  The full video for the model for layout a, b, and c are available at <https://youtu.be/5Y1hE4i7N2k>, <https://youtu.be/5Y1hE4i7N2k>, and <https://youtu.be/5Y1hE4i7N2k> respectively."

### 2024-09-10 paper.tex
Added Figure 11 title

\caption{\label{fig-five-gau-projs}(a) tSNE, (b) UMAP, and (c) PaCMAP}

>>>>

\caption{\label{fig-five-gau-projs}Model in \gD{}, on the layouts from
tSNE, UMAP, and PaCMAP (a1, b1, c1). Two views of the fit in projections
of each layout from \(4\text{-}D\), for the Gaussian cluster data. All
\gD{} models show five well-separated clusters with different gaps.
Layout a1 shows small separations, while layout b2 shows large gaps. On
the other hand, layout b3 shows average gaps with exact positions as in
\(4\text{-}D\). Assessing the different models fit for different layouts
for a specific cluster shows filled-out shape in a1, a2, and b1, b2. On
the other hand, c1 and c2 shows pancake shape. The full video for the
model for layout a, b, and c are available at
\url{https://youtu.be/5Y1hE4i7N2k}, \url{https://youtu.be/5Y1hE4i7N2k},
and \url{https://youtu.be/5Y1hE4i7N2k} respectively.}
